---
title: "p8105_hw1_yd2739"
author: "Yuxuan Du"
date: "2023-09-14"
output: github_document
---

```{r}
library(tidyverse)
```

## Problem 1
```{r}
library("moderndive")

data("early_january_weather")

variables = colnames(early_january_weather)

observation_num = nrow(early_january_weather)

variable_num = ncol(early_january_weather)

mean_temp = mean(pull(early_january_weather, temp))

q1_scatter = ggplot(data = early_january_weather, 
       mapping = aes(x = time_hour, y = temp, color = humid)) + 
  geom_point()

ggsave(
  'problem_1_scatter.png',
  plot = q1_scatter,
  device = png
)

q1_scatter
```

We could observe that in this plot, the temperature shows weak cyclic pattern
and  temperature's overall trend is increasing. The humidity didn't show any
trend according to the plot. 

the variables in the dataset are: `r variables`. 

Some of the important pattern in the dataset: the elements in columns
`origin`, `year`, `precip`, and `month` does not varies; There are lots on NA in `wind_gust`.

According to the help file, variables `year`, `month`, `day`, and `hour` are time of recording;`temp` and `dewp` are temperature and dewpoint in F; `humid` is the relative humidity; `wind_dir`, `wind_speed`, `wind_gus`t are variable that describe wind; 
`visib` is the visibility; `pressure` is the sea level pressure; `precip` is 
precipitation in inches.

the size of the data is `r observation_num` x `r variable_num`. 

the mean temperature is `r mean_temp` F degree. 

## Problem 2

#### Creating tibble
```{r}
set.seed(1234)
#create df of four variables, each with size of 10
Q2_df = tibble(
  samp_10_norm = rnorm(10),
  samp_10_norm_logic = samp_10_norm > 0,
  samp_char_vec = c('A', 'B', 'D', 'E', 'F', 'G', 'H', 'I', 'J', 'K'),
  samp_fac_vec = factor(c('red', 'red', 'red', 'red', 'red', 'red', 'blue', 'blue', 'yellow', 'yellow'))
)
Q2_df
```

#### Calculating means

```{r}
mean(pull(Q2_df, samp_10_norm))
mean(pull(Q2_df, samp_10_norm_logic))
mean(pull(Q2_df, samp_char_vec))
mean(pull(Q2_df, samp_fac_vec))
```

among the four vector, char vector and factor vector cannot take mean

#### Transform to numeric form

```{r, warning=FALSE, results = FALSE}
as.numeric(pull(Q2_df, samp_10_norm_logic))
as.numeric(pull(Q2_df, samp_char_vec))
as.numeric(pull(Q2_df, samp_fac_vec))
```
We could calculate the mean and transform to numeric for logic vector. 
This is reasonable since if logic can be transformed to numbers, we can calculate the mean.

For char vector, it says NAs introduced by coercion when executing, and it 
cannot be transformed to numeric vector. It is reasonable that we cannot calculate
the mean of char vector since we cannot change it to numeric form. 

But for factor vector, the  transformation to numeric form seems succeeded, but we still cannot calculate the mean. 
The transformation does not explain why we cannot calculate the mean of the factor vector.